Restrictive Clearance Comparison

### 2025-01-23 data-raw/RestrictiveClearance_comparison.Rmd
Re-structured analysis to fit new httk release and ensured that restrictive and non-restrictive estimates & parameterization are being appropriately handled.

```{r library_loading}
today <- format(Sys.Date(), "%d%b%Y")
devtools::load_all()
library(tidyverse)
library(ctxR)
library(ggvenn)
library(ggalluvial)
library(reticulate)
source("data-raw/RC_comparison_bkgd.R") # httk loaded here
```

```{r quick-fit}
# Only use plasma 
this_pk <- pk(cvt) +
  settings_optimx(method = "bobyqa") +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(
    keep_data_original = TRUE,
    suppress.messages = FALSE
  ) +
  scale_conc(dose_norm = TRUE, log10_trans = TRUE) +
  stat_error_model(error_group = vars(Chemical, Species))
this_pk <- do_fit(this_pk, n_cores = 12)
```

@@

```{r selecting_chemical_params}
chosen_list <- rat_pars_human
# The following are derived from the above selected list (see environment)
this_chem_v <- unique(chosen_list$param_df$Chemical)
this_param_list <- chosen_list$named_params
this_param_df <- chosen_list$param_df
this_httk_clearance_df <- chosen_list$clearance_df
this_species_v <- c("rat", "human")
```

@@

```{r venn_diagrams}
member_list <- list(
  httk_gas_pbtk = unique(get_cheminfo(info = "DTXSID",
                                species = "human",
                                model = "gas_pbtk",
                                median.only = TRUE,
                                physchem.exclude = TRUE,
                                suppress.messages = TRUE)) %>% 
    suppressWarnings(),
  cvt = cvt %>% filter(species %in% c("human", "rat")) %>% pull(analyte_dtxsid)
)

@@

ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
                         "RestrictiveClearance_Analysis/",
                         today, "httk_vs_CvT_VennDiagram_human.png"),
       bg = "white",
       height = 4, width = 6
)

# new_chems <- clipr::read_clip()
# length(unique(new_chems %in% setdiff(member_list$cvt, member_list$httk_gas_pbtk)))
# length(unique(new_chems %in% member_list$cvt))

# intersect(setdiff(member_list$cvt, member_list$httk_gas_pbtk), new_chems)

@@

Here I quickly check a few additional chemicals that will be added to _httk_.

```{r new_httk_chems}
new_chems_clint <- readxl::read_xlsx(path = paste0(Sys.getenv("OD_DIR"),
                                             "162Clint_Com_ChemID_DTXSID.xlsx"))
new_smiles <- readxl::read_xlsx(path = paste0(Sys.getenv("OD_DIR"),
                                             "127NewSMILES_Caco2_Cyprotex_7.23.24.xlsx"))
# New Clint
intersect(
  member_list$cvt[which(!(member_list$cvt %in% member_list$httk_gas_pbtk))], new_chems_clint$DTXSID
  )

# New SMILES
intersect(
  member_list$cvt[which(!(member_list$cvt %in% member_list$httk_gas_pbtk))], new_smiles$DTXSID
  )
```

@@

target_chem_info %>%
  ggplot(aes(x = monoisotopicMass)) +
  geom_histogram(binwidth = 20, fill = "grey5") +
  geom_vline(xintercept = 500, linetype = "longdash") +
  theme_bw()

@@

target_chem_lipinski %>%
  group_by(Lipinski) %>%
  count(`Mass <= 500 Da`, `H-donors < 5`, `H-acceptors < 10`, `logP < 5`,
        name = "Count") %>%
  ggplot(aes(
    axis3 = `Mass <= 500 Da`,
    axis4 = `logP < 5`,
    axis2 = `H-donors < 5`,
    axis1 = `H-acceptors < 10`,
    y = Count
  )) +
  geom_alluvium(aes(fill = Lipinski)) +
  geom_stratum() +
  scale_x_discrete(limits = c( 
    "H-acceptors < 10",
    "H-donors < 5",
    "<= 500 Da",
    "logP < 5"
  ),
  position = "top",
  expand = c(.2, .05)) +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  labs(title = "Overwhelmingly, this subset of chemicals passes Lipinksi's Rules of 5") +
  theme_minimal() +
  theme(axis.text.x = element_text(face = "bold", color = "black"),
        panel.grid = element_blank())

@@

```{r combine_tkstats}
# Start Here if you ran the background job
this_winmodel <- get_winning_model(this_pk)
this_tkstats <- inner_join(this_winmodel %>% filter(model != "model_flat"),
                          eval_tkstats(this_pk, finite_only = TRUE)) %>%
  filter(Media %in% "plasma",
         Chemical %in% this_chem_v,
         Species %in% this_species_v,
         !is.na(CLtot.tkstats)) %>%
  semi_join(get_winning_model(this_pk)) %>%
  dplyr::select(Chemical, Species, CLtot.tkstats, CLtot.nca) %>%
  distinct() %>%
  group_by(Chemical, Species, CLtot.tkstats) %>%
  summarize(
    CLtot.nca_mean = mean(CLtot.nca, na.rm = TRUE),
    CLtot.nca_sd = sd(CLtot.nca, na.rm = TRUE)
  )
message(length(unique(this_tkstats$Chemical)),
        " unique chemicals with finite clearance.")

@@

Finally, let's visualize where the tkstats predictions land.

```{r clearance_viz}
clearance_guess <- combined_clearance_df %>%
  mutate(AD_restrictive = abs(CLtot.tkstats - restrictive_clearance),
         AD_nonrestrictive = abs(CLtot.tkstats - nonrestrictive_clearance),
         rough_determination = ifelse(
           min(AD_restrictive, AD_nonrestrictive) == AD_restrictive &
             CLtot.tkstats < nonrestrictive_clearance,
           "Restrictive", "Possibly non-Restrictive"
         )) %>% 
  dplyr::ungroup()

>>>>

```{r library_loading}
today <- format(Sys.Date(), "%d%b%Y")
devtools::load_all()
library(tidyverse)
library(ctxR)
library(ggvenn)
library(ggalluvial)
library(flextable)
library(reticulate)
source("data-raw/RC_comparison_bkgd.R") # httk & dawson_2021 loaded here
```

I select which parameterization (based on species) that I will use.

```{r selecting_chemical_params}
chosen_list <- rat_pars_human
# The following are derived from the above selected list (see environment)
this_chem_v <- unique(chosen_list$param_df$Chemical)
this_param_rest_l <- chosen_list$named_params_restrictive
this_param_nrest_l <- chosen_list$named_params_nonrestrictive
this_param_df <- chosen_list$param_df
this_httk_clearance_df <- chosen_list$clearance_df
this_species_v <- c("rat", "human")
# Testing to make sure there are some chemicals that have different clearances
count(this_httk_clearance_df, restrictive_clearance == nonrestrictive_clearance)
# The majority (140) do!
```

Here I do a quick fit of the CvT data only for those that have plasma measurements.

```{r quick-fit}
# Only use plasma for simplicity
this_pk <- pk(cvt %>% filter(conc_medium_normalized == "plasma")) +
  settings_optimx(method = "bobyqa") +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(
    keep_data_original = TRUE,
    suppress.messages = FALSE) +
  scale_conc(dose_norm = TRUE, log10_trans = TRUE) +
  stat_error_model(error_group = vars(Chemical, Species))

this_pk <- do_prefit(this_pk)
this_pk <- do_fit(this_pk, n_cores = 14)
```

Relationships in the mathematical PK models:

- When there is only oral data available, `Fgutabs_Vdist` and `CLtot_Fgutabs`
will be calculated instead of the numerator alone.  
- $C_{ss} \cdot CL_{tot} = C_{H,u}\cdot CL{int}$ (Bennet & Sodhi 2024)  
- [Add More Here]

@@

@@

```{r venn_diagrams}
member_list <- list(
  httk_gas_pbtk = unique(get_cheminfo(info = "DTXSID",
                                species = "human",
                                model = "gas_pbtk",
                                median.only = TRUE,
                                physchem.exclude = TRUE,
                                suppress.messages = TRUE)) %>% 
    suppressWarnings(),
  cvt = cvt %>% 
    filter(species %in% c("human", "rat"),
           conc_medium_normalized == "plasma") %>%
    pull(analyte_dtxsid)
)

@@

ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
                         "RestrictiveClearance_Analysis/",
                         "CURRENT_", "httk_vs_CvT_VennDiagram_human.png"),
       bg = "white",
       height = 3, width = 5
)

@@

@@

target_chem_info %>%
  ggplot(aes(x = monoisotopicMass)) +
  geom_histogram(binwidth = 50, fill = "grey5",
                 boundary = 0) +
  geom_vline(xintercept = 500, linetype = "longdash") +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 100)) +
  theme_bw()

ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
                         "RestrictiveClearance_Analysis/",
                         "CURRENT_", "target_chems_molmass.png"),
       bg = "white",
       height = 3, width = 5
)

@@

target_chem_lipinski %>%
  group_by(Lipinski) %>%
  count(`Mass <= 500 Da`, `H-donors < 5`, `H-acceptors < 10`, `logP < 5`,
        name = "Count") %>%
  ggplot(aes(
    axis3 = `Mass <= 500 Da`,
    axis4 = `logP < 5`,
    axis2 = `H-donors < 5`,
    axis1 = `H-acceptors < 10`,
    y = Count
  )) +
  geom_alluvium(aes(fill = Lipinski)) +
  geom_stratum() +
  scale_x_discrete(limits = c( 
    "H-acceptors < 10",
    "H-donors < 5",
    "<= 500 Da",
    "logP < 5"
  ),
  position = "top",
  expand = c(.2, .05)) +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  labs(title = "Overwhelmingly, these chemicals passes Lipinksi's Rules of 5",
       fill = "Passes Lipinksi's Rules?") +
  scale_fill_manual(values = c("grey20", "green4")) +
  theme_minimal() +
  theme(axis.text.x = element_text(face = "bold", color = "black", size = 10),
        panel.grid = element_blank(),
        plot.title = element_text(hjust = 0.5),
        legend.position = "bottom")

ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
                         "RestrictiveClearance_Analysis/",
                         "CURRENT_", "Alluvium_Lipinski.png"),
       bg = "white",
       height = 4, width = 6
)
```

We also want to assess whether the "winning" _invivoPKfit_ fits are better than
the chosen _httk_ fit. This is a bit of a pre-requisite to our analysis of the
clearances and whether they are more or less reasonable in their reflection of
the reality. The metric used here will be RMSLE.

```{r httk_predictions}
restrictive_preds <- get_httk_preds(
  parameters = this_param_rest_l,
  pk_obj = this_pk,
  species = c("rat", "human")
) %>% rename_with(
  .fn = ~paste0(.x, "_restrictive"),
  .cols = starts_with("httk_")
)

nonrestrictive_preds <- get_httk_preds(
  parameters = this_param_nrest_l,
  pk_obj = this_pk,
  species = c("rat", "human")
) %>% rename_with(
  .fn = ~paste0(.x, "_nonrestrictive"),
  .cols = starts_with("httk_")
)

all_httk_preds <- inner_join(restrictive_preds, nonrestrictive_preds)

this_nonflat_winmodel <- get_winning_model(this_pk) %>%
  filter(model %in% c("model_1comp", "model_2comp"))

winning_preds <- predict(this_pk) %>%
  semi_join(this_nonflat_winmodel) %>%
  distinct(Chemical, Species, Chemical_Name,
           model, method, Dose, Media, Route, Reference, pLOQ, Time,
           N_Subjects, Conc, Conc_est)

# RMSLE formula
# LE = log1p(Conc_est) - log1p(Conc)
# SLE = LE^2
# RMSLE = sqrt(mean(SLE, na.rm = TRUE))

combined_preds <- all_httk_preds %>%
  left_join(winning_preds) %>%
  filter(!is.na(model))

combined_RMSLE <- combined_preds %>%
  ungroup() %>%
  mutate(
    restrictive_SLE = (log1p(httk_Preds_restrictive) - log1p(Conc))^2,
    nonrestrictive_SLE = (log1p(httk_Preds_nonrestrictive) - log1p(Conc))^2,
    invivoPK_SLE =  (log1p(Conc_est) - log1p(Conc))^2 
  ) %>%
  group_by(Chemical, Species) %>%
  summarize(RMSLE_restrictive = sqrt(mean(restrictive_SLE, na.rm = TRUE)),
            RMSLE_nonrestrictive = sqrt(mean(nonrestrictive_SLE, na.rm = TRUE)),
            RMSLE_invivoPKfit = sqrt(mean(invivoPK_SLE, na.rm = TRUE)))

combined_RMSLE %>%
  ungroup() %>%
  pivot_longer(cols = starts_with("RMSLE_"),
               names_to = "Source",
               values_to = "RMSLE") %>%
  mutate(Source = factor(Source,
                         levels = c("RMSLE_nonrestrictive",
                                    "RMSLE_invivoPKfit",
                                    "RMSLE_restrictive")
  )) %>%
  ggplot(aes(x = Source, y = RMSLE, group = Chemical)) +
  geom_point(alpha = 0.5) +
  geom_line(alpha = 0.5) +
  theme_bw()

combined_RMSLE %>%
  ungroup() %>%
  mutate(comparison_group = case_when(
    between(RMSLE_invivoPKfit, RMSLE_nonrestrictive, RMSLE_restrictive) |
     between(RMSLE_invivoPKfit, RMSLE_restrictive, RMSLE_nonrestrictive) ~ "Between",
    RMSLE_invivoPKfit < RMSLE_nonrestrictive &
      RMSLE_invivoPKfit < RMSLE_restrictive ~ "Less than",
    RMSLE_invivoPKfit > RMSLE_restrictive &
      RMSLE_invivoPKfit > RMSLE_nonrestrictive~ "More than"
  )) %>% 
  ggplot(aes(x = Chemical, y = RMSLE_invivoPKfit)) +
  geom_point(color = "green4") +
  geom_point(aes(y = RMSLE_nonrestrictive), shape = 4, size = 0.5) +
  geom_point(aes(y = RMSLE_restrictive), shape = 4, size = 0.5) +
  geom_linerange(aes(ymin = RMSLE_nonrestrictive, ymax = RMSLE_restrictive)) +
  facet_grid(~factor(comparison_group,
                     levels = c("Less than", "Between", "More than")),
             scales = "free_x", space = "free_x") +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid = element_blank())

ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
                         "RestrictiveClearance_Analysis/",
                         "CURRENT_", "RMSLE_comparison_fullChart.png"),
       bg = "white",
       height = 4, width = 8
)

@@

Another weight that we may consider is relative log-likelihood. This can be
calculated using AIC, compared to the the flat model.

```{r relative-likelihood}
this_rll_probs <- AIC(this_pk) %>%
  distinct(Chemical, Species, model, AIC) %>%
  pivot_wider(names_from = model, values_from = AIC) %>%
  rowwise() %>% 
  mutate(minAIC = min(c_across(starts_with("model_")), na.rm = TRUE)) %>% 
  ungroup() %>%
  mutate(across(starts_with("model_"), \(x) {
    signif(exp((minAIC - x)/2) * 100, 4)
  })) %>%
  mutate(across(starts_with("model_"), \(x) {
    ifelse(x < 1E-6, 0, x)
  })) %>%
  inner_join(this_nonflat_winmodel %>% distinct(Chemical, Species, model)) %>%
  ungroup() %>%
  filter(model_1comp >= 99 | model_2comp >= 99,
        model_flat < 1, Chemical %in% target_chems)

this_rll_probs %>%
  count(model_1comp >= 99, model_2comp >= 99)

The weights to be applied are calculated as such:

$$
\gamma = \frac{100\cdot \rm{RMSLE}}{\theta}
$$
Where $\theta$ is the relative log-likelihood. The smaller number the better.
If the RMSLE is zero, then it means that it is a "perfect" fit and we are highly
confident in using other metrics to gauge clearance. Below I put these together.

```{r model_weighting}
combined_model_weights <- combined_RMSLE %>%
  left_join(this_rll_probs) %>%
  ungroup() %>%
  pivot_longer(cols = starts_with("model_"),
               names_to = "all_models",
               values_to = "relative_likelihood") %>%
  filter(all_models == model) %>%
  ungroup() %>%
  mutate(gamma_weight = 100 * RMSLE_invivoPKfit / relative_likelihood,
         rmsle_comparison_group = case_when(
    between(RMSLE_invivoPKfit, RMSLE_nonrestrictive, RMSLE_restrictive) |
     between(RMSLE_invivoPKfit, RMSLE_restrictive, RMSLE_nonrestrictive) ~ "Between",
    RMSLE_invivoPKfit < RMSLE_nonrestrictive &
      RMSLE_invivoPKfit < RMSLE_restrictive ~ "Less than",
    RMSLE_invivoPKfit > RMSLE_restrictive &
      RMSLE_invivoPKfit > RMSLE_nonrestrictive~ "More than")
  ) %>%
  mutate(rmsle_comparison_group = factor(rmsle_comparison_group,
                                         levels = c("Less than", "Between",
                                                    "More than"))) %>%
  select(-all_models) %>% distinct()

Next we need to compare clearances. Sometimes this is difficult as the overlap
with certain calculations will be defined by the type of experimental data
available. For instance, if there is only oral data available, `CLtot.tkstats`
will _not_ be calculated and instead `CLtot/Fgutabs.tkstats` will be available.

```{r combine_tkstats}
# Get the winning model and only include chemicals in target_chems
this_winmodel <- get_winning_model(this_pk) %>%
    filter(Chemical %in% target_chems)
# How many overlapping chemicals have winning models that aren't flat?
count(
  this_winmodel,
  model
) # 153 = 97 1-compartment + 56 2-compartment

this_tkstats <- eval_tkstats(this_pk,
                             model = c("model_1comp", "model_2comp"),
                             finite_only = TRUE,
                             dose_norm = TRUE
) %>%
  rename(CLtot_Fgutabs.tkstats = `CLtot/Fgutabs.tkstats`) %>%
  distinct(Chemical, Species, method, model, Dose, Route, Media,
           CLtot.tkstats, CLtot_Fgutabs.tkstats, halflife.tkstats, Css.tkstats) %>%
  inner_join(this_winmodel)

count(
  this_tkstats,
  # model,
  !is.na(CLtot.tkstats),
  !is.na(CLtot_Fgutabs.tkstats),
  !is.na(halflife.tkstats)
) %>% flextable() %>%
  set_header_labels(
    `!is.na(CLtot.tkstats)` = "Valid Total Clearance",
    `!is.na(CLtot_Fgutabs.tkstats)` = "Valid Total Clearance/Fgutabs",
    `!is.na(halflife.tkstats)` = "Valid halflife",
    n = "Number of Chemicals"
    )
# 46 chemicals have valid total clearance
# 144 chemicals have valid total clearance/Fgutabs
# 5 chemicals have only valid total clearance and no valid total clearance/Fgutabs

count(this_tkstats, is.na(Css.tkstats))

Here I will evaluate $C_{SS}$, the steady-state concentration to get some
understanding of whether chemicals may be likely restrictive or non-restrictive.

```{r Css_assessment}

css_httk_batch <- function(param_list,
                           restrictive = TRUE) {
  stopifnot(is.logical(restrictive))

  css_list_r <- vapply(
    param_list,
    \(x) {
      calc_analytic_css_3comp2(parameters = x,
                               restrictive.clearance = restrictive)
    },
    FUN.VALUE = numeric(1L)
  )
  css_list_names <- names(param_list)

  css_df <- data.frame(Chemical = css_list_names,
                       Css_httk = css_list_r)
  if (restrictive) {
    css_df <- rename(css_df, Css_httk_r = Css_httk)
  } else {
    css_df <- rename(css_df, Css_httk_nr = Css_httk)
  }
  return(css_df)
}

this_css_df <- inner_join(
  css_httk_batch(this_param_rest_l, restrictive = TRUE),
  css_httk_batch(this_param_nrest_l, restrictive = FALSE)
) %>%
  inner_join(this_tkstats) %>%
  distinct(Chemical, model, Route, Css_httk_r, Css_httk_nr, Css.tkstats) %>%
  filter(Css_httk_nr > 0, Css_httk_r > 0, Css.tkstats > 0) %>%
  left_join(target_chem_lipinski %>% rename(Chemical = dtxsid)) %>%
  mutate(comparison_group_Css = factor(
    case_when(
      between(Css.tkstats, Css_httk_r, Css_httk_nr) |
        between(Css.tkstats, Css_httk_nr, Css_httk_r) ~ "Between",
      Css.tkstats < Css_httk_r & Css.tkstats < Css_httk_nr ~ "Below",
      Css.tkstats > Css_httk_r & Css.tkstats > Css_httk_nr ~ "Above"),
    levels = c("Above", "Between", "Below")
  ), Chemical = factor(Chemical) %>% fct_reorder(Css_httk_r)
  )

this_css_df %>%
  ggplot(aes(x = Chemical)) +
  geom_point(aes(y = Css_httk_r), shape = 4, size = 0.5) +
  geom_point(aes(y = Css_httk_nr), shape = 4, size = 0.5) +
  geom_linerange(aes(ymin = Css_httk_r,
                     ymax = Css_httk_nr)
  ) +
  geom_point(aes(y = Css.tkstats, shape = Route), color = "turquoise4") +
  facet_grid(rows = vars(comparison_group_Css),
             scales = "free_x",
             space = "free_x") +
  scale_y_log10(name = "Css") +
  scale_shape_manual(values = c(0,1)) +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid = element_blank())

ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
                         "RestrictiveClearance_Analysis/",
                         "CURRENT_", "Css_comparison_fullChart.png"),
       bg = "white",
       height = 4, width = 8
)

```{r}
this_css_df %>%
  distinct(Chemical, model, Route, Css_httk_r, Css_httk_nr, Css.tkstats) %>%
  filter(Css_httk_nr > 0, Css_httk_r > 0, Css.tkstats > 0) %>%
  left_join(data.frame(Chemical = names(this_param_rest_l),
                       CLint = vapply(names(this_param_rest_l),
                                      \(x) {
                                        this_param_rest_l[[x]][["Clint"]]
                                      },
                                      FUN.VALUE = numeric(1L)
                       ))) %>%
  mutate(CLint = log10(CLint + 1)) %>%
  ggplot(aes(x = CLint)) +
  geom_point(aes(y = Css_httk_r), shape = 4, size = 0.5) +
  geom_point(aes(y = Css_httk_nr), shape = 4, size = 0.5) +
  geom_linerange(aes(ymin = Css_httk_r,
                     ymax = Css_httk_nr)
  ) +
  scale_y_log10(name = "C<sub>SS</sub>") + 
  labs(x = "CL<sub>int</sub>") +
  geom_point(aes(y = Css.tkstats, shape = Route), color = "turquoise4") +
  scale_shape_manual(values = c(0,1)) +
  theme_bw() +
  theme(axis.title = ggtext::element_markdown())

ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
                         "RestrictiveClearance_Analysis/",
                         "CURRENT_", "Css_x_CLint.png"),
       bg = "white",
       height = 4, width = 8
)
```

Now I will try to triangulate the model weights witht the Css estimates.

```{r weighted_Css}
combined_model_weights %>%
  inner_join(this_css_df) %>%
  ggplot(aes(x = fct_reorder(Chemical, Css_httk_r))) +
  geom_point(aes(y = Css_httk_r), shape = 4, size = 0.5) +
  geom_point(aes(y = Css_httk_nr), shape = 4, size = 0.5) +
  geom_linerange(aes(ymin = Css_httk_r,
                     ymax = Css_httk_nr)
  ) +
  geom_point(aes(y = Css.tkstats, shape = Route, color = gamma_weight)) +
  facet_grid(rows = vars(comparison_group_Css),
             cols = vars(rmsle_comparison_group),
             scales = "free_x",
             space = "free_x") +
  scale_y_log10(name = "Css") +
  scale_shape_manual(values = c(0,1)) +
  scale_color_viridis_b(option = "viridis", 
                        guide = guide_colorbar(position = "bottom")) +
  labs(subtitle = "RMSLE for invivoPKfit compared to httk predictions",
       x = "Chemical\n(ordered by increasing restrictive Css prediction)",
       y = "Css",
       color = "Inverse Confidence") +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        plot.subtitle = element_text(hjust = 0.5),
        panel.grid = element_blank(),
        legend.title = element_text(vjust = 0.8))

ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
                         "RestrictiveClearance_Analysis/",
                         "CURRENT_", "Css_withRMSLEweights.png"),
       bg = "white",
       height = 5, width = 10
)

```{r calc_CLtot_Fgutabs}
this_tkstats2 <- this_tkstats %>%
  left_join(
    this_param_df %>%
      distinct(Chemical, Species, Fabsgut.restrictive)
  ) %>%
  mutate(CLtot_calc = CLtot_Fgutabs.tkstats * Fabsgut.restrictive)

ggplot(data = this_httk_clearance_df,
       aes(x = Chemical)) +
  geom_point(aes(y = restrictive_clearance), color = "green4") +
  geom_point(aes(y = nonrestrictive_clearance), color = "orange2") +
  geom_point(data = this_tkstats2,
             aes(y = CLtot_calc)) +
  scale_y_log10() +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank())

@@

Finally, let's visualize where the tkstats predictions land.
Because there are only a handful of chemicals which _invivoPKfit_ can calculate
`CLtot` for, I will employ two strategies to gauge how different these estimates
are in reality.

1. Visualize differences in half-life.  
2. Multiply `CLtot_Fgutabs` by the `Fabsgut` value parameterized in _httk_ to
get a clearance value.

```{r half-life}
combined_clearance_df %>%
  ggplot(aes(x = halflife.tkstats)) +
  geom_point(aes(y = restrictive_halflife), color = "magenta2") +
  geom_point(aes(y = nonrestrictive_halflife), color = "green4") +
  coord_equal(xlim = c(0, 200), y = c(0, 200))
```

Notes:
Look at Css values for restrictive/nonrestrictive (httk solutions)
AICs for models

```{r clearance_viz}

this_param_df %>%
  distinct(Chemical, Species, Fabsgut.restrictive, Fabsgut.nonrestrictive) %>%
  inner_join(combined_clearance_df) %>%
  mutate(CLtot.nonrest = CLtot_Fgutabs.tkstats * Fabsgut.nonrestrictive,
         CLtot.rest = CLtot_Fgutabs.tkstats * Fabsgut.restrictive) %>%
  pivot_longer(cols = c(restrictive_clearance, nonrestrictive_clearance,
                        CLtot.nonrest, CLtot.rest),
               names_to = "Source",
               values_to = "Clearance") %>%
  ggplot(aes(y = Chemical, x = Clearance, color = Source)) +
  geom_point() +
  labs(title = "comparison of restrictive and non-restrictive clearance estimates") +
  theme_bw() +
  coord_cartesian(xlim = c(0.0001, 1000)) +
  scale_x_log10()

this_param_df %>%
  distinct(Chemical, Species, Fabsgut.restrictive, Fabsgut.nonrestrictive) %>%
  inner_join(combined_clearance_df) %>%
  mutate(nonrest_fgutabs = nonrestrictive_clearance / Fabsgut.nonrestrictive,
         rest_fgutabs = nonrestrictive_clearance / Fabsgut.restrictive) %>%
  pivot_longer(cols = c(CLtot_Fgutabs.tkstats,
                        rest_fgutabs, nonrest_fgutabs),
               names_to = "Source",
               values_to = "Clearance") %>%
  ggplot(aes(y = Chemical, x = Clearance, color = Source)) +
  geom_point() +
  labs(title = "comparison of restrictive and non-restrictive clearance estimates") +
  theme_bw() +
  coord_cartesian(xlim = c(0.000001, 100000)) +
  scale_x_log10()

this_param_df %>%
  distinct(Chemical, Species, Fabsgut.restrictive, Fabsgut.nonrestrictive) %>%
  inner_join(combined_clearance_df) %>%
  mutate(nonrest_fgutabs = nonrestrictive_clearance / Fabsgut.nonrestrictive,
         rest_fgutabs = nonrestrictive_clearance / Fabsgut.restrictive) %>%
   mutate(AD_restrictive = abs(CLtot_Fgutabs.tkstats - rest_fgutabs),
         AD_nonrestrictive = abs(CLtot_Fgutabs.tkstats - nonrest_fgutabs),
         rough_determination = ifelse(
           min(AD_restrictive, AD_nonrestrictive) == AD_restrictive &
             CLtot.tkstats <= nonrest_fgutabs,
           "Restrictive", "Possibly non-Restrictive"
         )) %>% 
  dplyr::ungroup() %>% View()

clearance_guess <- combined_clearance_df %>%
  mutate(AD_restrictive = abs(CLtot.tkstats - restrictive_clearance),
         AD_nonrestrictive = abs(CLtot.tkstats - nonrestrictive_clearance),
         rough_determination = ifelse(
           min(AD_restrictive, AD_nonrestrictive) == AD_restrictive &
             CLtot.tkstats < nonrestrictive_clearance,
           "Restrictive", "Possibly non-Restrictive"
         )) %>% 
  dplyr::ungroup()
